Qualifying Report

### 2019-01-07 Source/QualifyingReport/QualifyingReport.tex
edited QR
AM work on QR

\subsubsection{Patient Health Questionnaire)}
The Patient Health Questionnaire is a nine-item questionnaire Likert scale which is designed to measure a 
\subsubsection{WASI}
\subsubsection{Digit Span}
\subsubsection{Rey Auditory-Verbal learning test}

\subsubsection{Digit Symbol Substitution Test}
The digit symbol test involves a key consisting of the numbers 1-9 and a corresponding unique symbol. Below this key is a series of numbers from 1-9 in a randomized order and repeated multiple times. The participant is asked to fill in the corresponding symbol for each number. The task requires that the participant move between the key and the randomized sequence such that  they may retrieve the correct answer from the key, hold this in short-term memory and transcribe the key in the appropriate place.

\subsubsection{Corsi Block Tapping Task}
The original Corsi apparatus consists of a series of nine blocks arranged irregularly on a 9 x 11in board. The blocks are tapped by the adminstrator in a randomized sequence of increasing length. Immediately after each sequence is demonstrated, the task is to mirror the sequence back to the adminstrator with the sequences increasing in length until a mistake is made. 
\subsubsection{Verbal Fluency}
%% In this paragraph cite Henry et al, 2004 - taken from Taler and Phillips (2008) - Henry et al, 2004 is a meta analysis
There are a number of tests that characterise this category of verbal fluency, but generally fall into two categories. Letter (Phonemic) fluency involves the generation of as many words as possible which begin with a specified letter. Category fluency involves the generation of as many words as possible that fall into a specfied category. Both these tasks impose demands on a number of different cognitive processes namely, executive function, verbal retrieval and recall, giving appropriate answers while monitoring previous answers and inhibit inappropriate responses. However, these two tasks require different strategies when attempting them. Letter fluency relies on search strategies based on lexical representations whereas category fluency requires a search for semantic extensions of a superordinate term, meaning that semantic associations within the lexicon must be intact in order for the task to be carried out successfully. \par  
There have been numerous studies which have documented the impact that AD has on verbal fluency tests in both categories. A review carried out by Henry et al, found that performance in both letter fluency and category fluency was impaired in those with AD vs controls, but found a larger effect for tests of semantic fluency.
\subsubsection{Naming Tests}
Word-finding difficulty is a common symptom of AD and these deficits usually occur during the early stages of the disease progression. As such , a test of a patients ability to find words (known as confrontation naming) is a common way to measure cognitive decline. One common way to do this is the Boston Naming Test (BNT) which comprises 60 items on a spectrum of very frequent to very infrequent. This has been reduced subsequently to two thirty item versions and four fifteen item versions, which correlate significantly with the original sixty item version and the benefit of the shorter versions of the test is that it facilitates testing of individuals with AD who may suffer from fatigue or limited attention span.

Whilst these studies and tests provide evidence that there are word finding difficulties in those with MCI, on their own they do not provide sufficient ability to diagnose MCI or provide an prognosis of disease progression.
\subsubsection{Wisconsin Card Sorting}
\subsubsection{Complex Figure Task}
\subsubsection{Narrative Description Task}
\subsubsection{Sentence Completion Task}
\subsubsection{Serial Non-word Repetition}
\subsubsection{Grooved Pegboard Test}
The Grooved Pegboard Test (GPT) was originally designed to cover a variety of different psycho-motor functions including hand-eye coordination and motor speed. However, some studies have shown a correlation of performance in the GPT and measures of cognitive performance such as the Montreal Cognitive Assessment.  
\subsubsection{Visual Search}
In research, there have been shown to be deficits in both AD and MCI populations. Whilst these deficits were not as apparent in MCI populations, there remained a difference that could be used to differentiate healthy controls from those with MCI.
% Abnormal Visual Search in MCI and Alzheimer's Disease. Tales.A 2005

>>>>

\subsubsection{Digit Span Test}
The Digit Span Test is predominantly used to measure a person's working memory capacity, specifically the capacity used to store and recall numbers. A participant is presented with a series of numbers of fixed length and is asked to recall those numbers in normal or reverse order. The series of numbers gets progressively longer until such time as a participant fails three or more times out of eight presentations.
% Muangpaisan - Digit span and verbal fluency tests in patients with MCI and normal subjects in Thai community.
MCI patients had significantly lower digit span score, in both normal and reverse order versions of this test. Research has shown that Digits Backwards can, to some degree, predict a diagnosis of MCI. They found that Age, Gender and Education have an impact on the performance of the tests.
% Emrani - Assessing Working Memory in Mild Cognitive Impairment with Serial Order Recall
Found no differences between specifically amnestic MCI and controls, but could differentiate between Mixed MCI and the other groups with mixed MCI recalling fewer correct responses than other groups. Notably, there was an attenuated recency effect in those with mixed MCI.
% Kessels - Assessment of Working-memory deficits in patients with MCI and AD using Wechsler's Working Memory Index which includes digit span.
Kessels identifies that that there are working memory deficits in MCI patients and these worsen with AD patients.
% Kessels - Assessment of verbal and visuospatial working memory in MCI and AD.
Kessels identifies that both MCI and AD have impaired performance on all three conditions of the digit span test. No differences were found between forward and backward conditions in any of the groups. However, available tests may not detect subtle impairments.
\subsubsection{Rey Auditory-Verbal learning test}
Rey's Auditory Verbal Learning Test (RAVLT+) looks a wide range of neuropsychological processess including short-term auditory-verbal memory, retention of information. Participants are given a list of 15 unrelated words, repeated over five different trials and are asked to repeat. Another list of 15 unrelated words are given and the client must again repeat the original list of 15 words and then again after 30 minutes. 
% Moradi - Rey's Auditory Verbal Learning Test scores can be predicted from whole brain MRI in AD.
Several studies have shown that an impairment in RAVLT score reflect well the underlying pathology caused by AD. Thus making the RAVLT an effective early marker to detect AD in persons with memory complaints. Moradi investigated to what extent the RAVLT scores are predictable based on MRI data using machine learning approaches, as well as to find out what the most important brain regions are for the estimation of RAVLT scores. They found a highly significant cross validated correlation between the estimated and observed RAVLT immediate and RAVLT Percent Forgetting. Further, they found that the conversion of MCI subjects to AD in 3-years could be predicted based on either observed or estimated RAVLT scores with an accuract comparible to MRI-based biomarkers.
% Schoenberg - Test performance and classification statistics for the Rey Auditory Verbal Learning Test in selected clinical samples.
Study found that RAVLT to best distguish patients suspected of Alzheimer's disease from the psychiatric comparison group.
\subsubsection{Digit Symbol Substitution Test}
The Digit Symbol Substitution Test (DSST) involves a key consisting of the numbers 1-9 and a corresponding unique symbol. Below this key is a series of numbers from 1-9 in a randomized order and repeated multiple times. The participant is asked to fill in the corresponding symbol for each number. The task requires that the participant move between the key and the randomized sequence such that  they may retrieve the correct answer from the key, hold this in short-term memory and transcribe the key in the appropriate place.
% Rosano - Digit symbol substitution test and future clinical and subclinical disorders of cognition, mobility and mood in older adults.
Among those with no disorder in cognition, mobility and mood, being in the lowest DSST quartile compared to the highest was associated with nearly twice the odds of developing one or more clinical or subclinical disorders. Associations were stronger for incident clinical disorders in cognition. Slower psychomotor speed may serve as a biomarker of risk of clinical disorders, mobility and mood. While in part attributable to vascular brain disease, other potentially modifiable contributors may be present. Further studying the causes of psychomoto slowing with ageing might provide novel insights into age-related brain disorders.
% Pascoe - The symbol-digit modalities test in MCI: Evidence from Parkinson's Disease Patients.
Pascoe compared patients with PD with Normal Cognition (PD-N) with those with PD and MCI (PD-MCI) and healthy participants. PD-MCI pariticipants achieved significantly lower scores than other groups in the DSST task.  
\subsubsection{Corsi Block Tapping Task}
The original Corsi apparatus consists of a series of nine blocks arranged irregularly on a 9 x 11in board. The blocks are tapped by the adminstrator in a randomized sequence of increasing length. Immediately after each sequence is demonstrated, the task is to mirror the sequence back to the adminstrator with the sequences increasing in length until a mistake is made.
% Perrochon - How specific are cognitive deficits in short-term visuospatial memory in mild cognitive impairment patients?
The CBT performances were significantly less satisfactory in the multi-domain MCI category than in other groups (Healthy adults, Amnesic MCI and Non-amnesic MCI with executive function impairment).  
\subsubsection{Verbal Fluency}
%% In this paragraph cite Henry et al, 2004 - taken from Taler and Phillips (2008) - Henry et al, 2004 is a meta analysis
There are a number of tests that characterise this category of verbal fluency, but generally fall into two categories. Letter (Phonemic) fluency involves the generation of as many words as possible which begin with a specified letter. Category fluency involves the generation of as many words as possible that fall into a specfied category. Both these tasks impose demands on a number of different cognitive processes namely, executive function, verbal retrieval and recall, giving appropriate answers while monitoring previous answers and inhibit inappropriate responses. However, these two tasks require different strategies when attempting them. Letter fluency relies on search strategies based on lexical representations whereas category fluency requires a search for semantic extensions of a superordinate term, meaning that semantic associations within the lexicon must be intact in order for the task to be carried out successfully. \par  
There have been numerous studies which have documented the impact that AD has on verbal fluency tests in both categories. A review carried out by Henry et al, found that performance in both letter fluency and category fluency was impaired in those with AD vs controls, but found a larger effect for tests of semantic fluency.
\subsubsection{Naming Tests}
Word-finding difficulty is a common symptom of AD and these deficits usually occur during the early stages of the disease progression. As such , a test of a patients ability to find words (known as confrontation naming) is a common way to measure cognitive decline. One common way to do this is the Boston Naming Test (BNT) which comprises 60 items on a spectrum of very frequent to very infrequent. This has been reduced subsequently to two thirty item versions and four fifteen item versions, which correlate significantly with the original sixty item version and the benefit of the shorter versions of the test is that it facilitates testing of individuals with AD who may suffer from fatigue or limited attention span.

Whilst these studies and tests provide evidence that there are word finding difficulties in those with MCI, on their own they do not provide sufficient ability to diagnose MCI or provide an prognosis of disease progression.
\subsubsection{Wisconsin Card Sorting}

\subsubsection{Complex Figure Task}

\subsubsection{Narrative Description Task}

\subsubsection{Sentence Completion Task}

\subsubsection{Serial Non-word Repetition}

\subsubsection{Grooved Pegboard Test}
The Grooved Pegboard Test (GPT) was originally designed to cover a variety of different psycho-motor functions including hand-eye coordination and motor speed. However, some studies have shown a correlation of performance in the GPT and measures of cognitive performance such as the Montreal Cognitive Assessment.  
\subsubsection{Visual Search}
In research, there have been shown to be deficits in both AD and MCI populations. Whilst these deficits were not as apparent in MCI populations, there remained a difference that could be used to differentiate healthy controls from those with MCI.
% Abnormal Visual Search in MCI and Alzheimer's Disease. Tales.A 2005
